---
title: "Workout 3 Binomial"
author: "Raina Yang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to Binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(workout03)
```

## Purpose of Package workout3: binomial

The purpose of this package "workout3" is to create an R package that implements functions for calculating probabilities of a Binomial random variable, and related calculations such as the probability distribution, the expected value, variance, etc.



## Calculations and Functions
The following functions are main functions for calculations.
– bin_choose()
– bin_probability() 
– bin_distribution() 
– bin_cumulative()

bin_choose() that calculates the number of
combinations in which k successes can occur in n trials.
such as
```{r}
bin_choose( 5, 2 )== 10
```

bin_probability() takes three arguments: success, trials, and prob.

such as
```{r}
# probability of getting 2 successes in 5 trials
# (assuming prob of success = 0.5) 
bin_probability( 2, 5, 0.5)
```


bin_distribution() has two arguments trials, and prob.

such as
```{r}
 # binomial probability distribution
dis1 <- bin_distribution( 5, 0.5) 
dis1
```


bin_cumulative() has two arguments trials, and prob.

such as
```{r}
 # binomial cumulative distribution
bin_cumulative( 5, 0.5)
```


## Plot and summary
By using the function plot or summary, the user can generate systematic summary or visual information regarding the data.

for instance
```{r}

# plotting binomial probability distribution
dis1 <- bin_distribution( 5, 0.5) 
plot(dis1)

# plotting binomial cumulative distribution
dis2 <- bin_cumulative( 5,  0.5) 
plot(dis2)

 bin1 <- bin_variable( 10,  0.3) 
 bin1
 binsum1 <- summary(bin1)
binsum1
 
```

